Comparing Models of Delta-Notch Signalling

### 2025-04-08 snacks-presentation/main.tex
Add a bunch of .jpg slides.

% SECTION 2: DORA (15m?)
\section{Derivation}

\begin{frame}{Preliminaries and Assumptions}
\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{image0.png}
\end{figure}
    Table 1: A list of possible reactions and their rates in a cell $A$ with neighbour $B$.
\end{frame}

@@

\begin{frame}{Matrix Formulation}
To construct the matrix $\mathbf{A}$, we first establish a one-to-one mapping between the three-dimensional state space $(n,d,i)$ and a one-dimensional index $k$. \\~\\
We set $n_{max}$, $d_{max}$, and $i_{max}$ as large enough bounds for Notch, Delta, and NICD in cell $A$. These define the size of our 3D ``box" of possible states. \\
\textit{Remark:} These are not strict limits but chosen large enough to technically capture all relevant dynamics.
\end{frame}

@@

\[
A_{k,k} = -v=-[H^+(i) + H^-(i) + \gamma n + \gamma d + \gamma_I i + k_T n D_{ext} + k_T d N_{ext}]
\]

where $(n,d,i)$ is the state corresponding to index $k$.\\

@@

\begin{align*}
\mathbf{A} = 
\begin{pmatrix}
-v_{000} & \alpha_{000,001} & \alpha_{000,010} & \alpha_{000,011} & \alpha_{000,100} & \alpha_{000,101} & \alpha_{000,110} & \alpha_{000,111} \\
\alpha_{001,000} & -v_{001} & \alpha_{001,010} & \alpha_{001,011} & \alpha_{001,100} & \alpha_{001,101} & \alpha_{001,110} & \alpha_{001,111} \\
\alpha_{010,000} & \alpha_{010,001} & -v_{010} & \alpha_{010,011} & \alpha_{010,100} & \alpha_{010,101} & \alpha_{010,110} & \alpha_{010,111} \\
\alpha_{011,000} & \alpha_{011,001} & \alpha_{011,010} & -v_{011} & \alpha_{011,100} & \alpha_{011,101} & \alpha_{011,110} & \alpha_{011,111} \\
\alpha_{100,000} & \alpha_{100,001} & \alpha_{100,010} & \alpha_{100,011} & -v_{100} & \alpha_{100,101} & \alpha_{100,110} & \alpha_{100,111} \\
\alpha_{101,000} & \alpha_{101,001} & \alpha_{101,010} & \alpha_{101,011} & \alpha_{101,100} & -v_{101} & \alpha_{101,110} & \alpha_{101,111} \\
\alpha_{110,000} & 0 & H^+(0) & 0 & H^-(1) & 0 & -v_{110} & \gamma_I \\
\alpha_{111,000} & 0 & 0 & H^+(0) & 0 & H^-(1) & H^+(1) & -v_{111}
\end{pmatrix}
\end{align*}

where:
\[
\alpha_{ndi,n'd'i'} = H^+(i) + H^-(i) + \gamma n + \gamma d + \gamma_I i + k_T n D_{ext} + k_T d N_{ext}
\]

@@

\begin{itemize}
    \item A one-cell system: $P(n,d,i,t+\Delta t)$ \\
    A $k$-cell system: $P(n_1,d_1,i_1,n_2,d_2,i_2,...,n_k,d_k,i_k,t+\Delta t)$\\
    \item $D_{ext}$ (the average Delta concentration over all neighbours of cell $A$).
\end{itemize}
\vfill
\pause
The complexity of a single cell highlights the need for numerical methods to model interactions between cells.
\end{frame}

>>>>

% SECTION 2: DORA (15m?)
\section{Derivation}
\begin{frame}{Preliminaries and Assumptions}
\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{image0.png}
\end{figure}
    Table 1: A list of possible reactions and their rates in a cell $A$ with neighbour $B$.
\end{frame}

@@

\begin{frame}{Matrix Formulation}
To construct the matrix $\mathbf{A}$, we first establish a one-to-one mapping between the three-dimensional state space $(n,d,i)$ and a one-dimensional index $k$. \\~\\

We set $n_{max}$, $d_{max}$, and $i_{max}$ as large enough bounds for Notch, Delta, and NICD in cell $A$. These define the size of our 3D ``box" of possible states. \\
\textit{Remark:} These are not strict limits but chosen large enough to technically capture all relevant dynamics.
\end{frame}

@@

\[
A_{k,k} = -v_k =-[H^+(i) + H^-(i) + \gamma n + \gamma d + \gamma_I i + k_T n D_{ext} + k_T d N_{ext}]
\]

where $(n,d,i)$ is the state corresponding to index $k$.\\
\textit{Recall:} We assume that reaction times follow a Poisson point process.\\~\\

\pause

@@

\small \begin{align*}
\mathbf{A} = 
\begin{pmatrix}
-v_{000} & \alpha_{000,001} & \alpha_{000,010} & \alpha_{000,011} & \alpha_{000,100} & \alpha_{000,101} & \alpha_{000,110} & \alpha_{000,111} \\
\alpha_{001,000} & -v_{001} & \alpha_{001,010} & \alpha_{001,011} & \alpha_{001,100} & \alpha_{001,101} & \alpha_{001,110} & \alpha_{001,111} \\
\alpha_{010,000} & \alpha_{010,001} & -v_{010} & \alpha_{010,011} & \alpha_{010,100} & \alpha_{010,101} & \alpha_{010,110} & \alpha_{010,111} \\
\alpha_{011,000} & \alpha_{011,001} & \alpha_{011,010} & -v_{011} & \alpha_{011,100} & \alpha_{011,101} & \alpha_{011,110} & \alpha_{011,111} \\
\alpha_{100,000} & \alpha_{100,001} & \alpha_{100,010} & \alpha_{100,011} & -v_{100} & \alpha_{100,101} & \alpha_{100,110} & \alpha_{100,111} \\
\alpha_{101,000} & \alpha_{101,001} & \alpha_{101,010} & \alpha_{101,011} & \alpha_{101,100} & -v_{101} & \alpha_{101,110} & \alpha_{101,111} \\
\alpha_{110,000} & \alpha_{110,001} & \alpha_{110,010} & \alpha_{110,011} & \alpha_{110,100} & \alpha_{110,101} & -v_{110} & \alpha_{110,111} \\
\alpha_{111,000} & \alpha_{111,001} & \alpha_{111,010} & \alpha_{111,011} & \alpha_{111,100} & \alpha_{111,101} & \alpha_{111,110} & -v_{111}
\end{pmatrix}
\end{align*}

where:
\begin{align*}
\alpha_{ndi,n'd'i'} = 
\begin{cases}
H^+(i) + H^-(i) + \gamma n + \gamma d + \gamma_I i + k_T n D_{ext} + k_T d N_{ext} & \text{if } (n,d,i) \rightarrow (n',d',i') \\
0 & \text{otherwise}
\end{cases}
\end{align*}

@@

\begin{itemize}
    \item A one-cell system: $P(n,d,i,t+\Delta t)$ \\
    A $k$-cell system: $P(n_1,d_1,i_1,n_2,d_2,i_2,...,n_k,d_k,i_k,t+\Delta t)$\\
    \item $D_{ext}$ (the average Delta concentration over all neighbours of cell $A$)\\ can vary depending on the choice of domain.
\end{itemize}
\vfill
\pause
The complexity of a single cell highlights the need for numerical methods to model interactions between cells.
\end{frame}
